\addcontentsline{toc}{chapter}{Abstract}\vspace{-1cm}
%Border
\begin{tikzpicture}[remember picture, overlay]
  \draw[line width = 4pt] ($(current page.north west) + (0.75in,-0.75in)$) rectangle ($(current page.south east) + (-0.75in,0.75in)$);
\end{tikzpicture}


\acrfull{sap} is an ERP (Enterprise Resource Planning) based software product company that supports and
manages business operations and customer relations of all types of companies, big to small scale.
SAP is a leading provider of cloud computing, enterprise mobility, and analytics to government and non-profit agencies worldwide. 

The SAP for Public Sector innovative solution portfolio to improve government performance, services, and accountability to improve people’s lives.
In the public sector, citizen engagement and service delivery operations are also becoming increasingly more complicated too. Government has a timeless mission to protect, provide, and prosper. Around the world, government organizations are trying to provide their citizens with economic opportunity, health care access, a sustainable environment, and better educational systems and infrastructure.

The frontend of the web application is built using SAP UI5 and SAP Fiori principles. The database
is configured on the in-memory, column-oriented SAP S/4 /acrshort{hana} Database, which helps in fast
retrieval and efficient storage of the data. Backend server-side coding is based on SAP Core \acrfull{abap}
(Advanced Business Application Programming Language), which is a 4th generation
programming language. Core Data Service Views are used for efficient data modelling. Frontend
and Backend services are connected via SAP OData and SAP Gateway.


\pagebreak